Hybrid platforms and bargaining power

### 2024-05-12 src/paper/application.tex
Change notation (F_F -> K_F)

There is an infinite measure of fringe firms, who are deciding whether to enter the market.
Entering has two, separate costs: an exogenous investment cost $I_F$, and the lump-sum platform entry fee $F_F$.
One can conceptualize the first as usual fixed costs, such as the cost of setting up production, or designing a product.
Meanwhile, the second is a payment to the platform for using its services.
While percentage fees are more common both in the literature and in practice, I assume a lump-sum fee for a few reasons.
First, and most importantly, revenue-based fees enter the entrants' pricing decision, and thus create a channel through which platforms distort competition.
I want to show that even in the absence such distortions, hybrid platforms can have a significant impact on competition.
Furthermore, due to this distortion, the resulting game could not be represented as a transferable utility game, and the proposed solution concept would not be applicable.
Finally, lump-sum fees do make sense in settings when individual negotiation takes place and contracts are not standardized.

In the benchmark model, the game starts by the platform announcing and committing to an entry fee $F_F$.\footnote{
    With no commitment power, but the ability to set any prices after fringe firms make their investment decisions, the platform would charge an entry fee that would make the fringe profits zero \emph{sans the investment cost}.
    This would lead to a trivial equilibrium, where no firm enters.
}
In the bargaining case, the platform cannot commit to entry fees at this point.
Next, each fringe firm decides whether to create a product at cost $I_F$ and enter the market.
In the bargaining model, the entry fee is decided at this point as a result of some negotiation\footnote{
    The negotiation process, or rather its outcome is described in detail in \cref{sec:cooperative_game}.
} between the platform and the firms that have made the investment.
After this, the firms that made the investment pay the platform entry fees, too.

@@

The main difference between the benchmark and the bargaining model is in determining the entry fee $F_F$.
In the former, the platform unilaterally sets the fee, and the fringe treats it as a take it or leave it offer.
On the other hand, in the bargaining model, I assume that the entry fee is the result of a negotiation between the parties.
\Cref{fig:timing} illustrates this difference.

\begin{figure}
    \centering
    \begin{subfigure}{0.45\textwidth}
        \centering
        \begin{tikzpicture}[node distance=2cm, auto]
            \node[align=center] (entry_fee) {Platform unilaterally sets the entry fee \\ $[F_F]$};
            \node[align=center] (entry_decision) [below of=entry_fee] {Potential entrants decide to enter \\ at cost $I_F + F_F$ \\ $[N_F]$};
            \node[align=center] (sales) [below of=entry_decision] {Platform and fringe sell products \\ $[\pi_{Fi}^v, \pi_P^v]$};
            \node[align=center] (final) [below of=sales] {Final profits are realized \\ $[\pi_{Fi}^t, \pi_P^t]$};
            \draw[->] (entry_fee) -- (entry_decision);
            \draw[->] (entry_decision) -- (sales);
            \draw[->] (sales) -- (final);
        \end{tikzpicture}
        \caption{Benchmark model (platform sets the entry fee unilaterally)}
    \end{subfigure}
    \hfill
    \begin{subfigure}{0.45\textwidth}
        \centering
        \begin{tikzpicture}[node distance=2cm, auto]
            \node[align=center] (entry_decision) {Potential entrants decide to invest \\ at cost $I_F$ \\ $[N_F]$};
            \node[align=center] (entry_fee) [below of=entry_decision] {Entry fees are negotiated \\ between platform and $N_F$ fringe firms \\ $[F_F]$};
            \node[align=center] (sales) [below of=entry_fee] {Platform and fringe sell products \\ $[\pi_{Fi}^v, \pi_P^v]$};
            \node[align=center] (final) [below of=sales] {Final profits are realized \\ $[\pi_{Fi}^t, \pi_P^t]$};
            \draw[->] (entry_decision) -- (entry_fee);
            \draw[->] (entry_fee) -- (sales);
            \draw[->] (sales) -- (final);
        \end{tikzpicture}
        \caption{Bargaining model (platform and fringe negotiate over the entry fee)}
    \end{subfigure}
    \caption{Timing of the models}
    \label{fig:timing}
\end{figure}

@@

I assume that there is a continuum of potential fringe entrants, indexed by $i \in \mathbb{R}^+_0$.
Each of them can create a product at an exogenous investment cost $I_F$.
If they decide not to, they make zero profits and do not participate in the later stages of the game.
Furthermore, these firms can only sell their products through the platform, for which the platform can charge a lump-sum entry fee $F_F$.
The timing of these decisions is as follows: (1) the platform sets and commits to an entry fee $F_F$, (2) the fringe firms decide whether to enter the market, and (3) the firms that have entered pay the entry fee to the platform.

@@

In order to keep the model tractable I model the negotiation process in a reduced form manner.
In particular, I assume that the platform and the entrants agree on an entry fee $F_F$, which makes the total profits net entry fees equal to the Shapley value of the players.\footnote{
    One simple extension would be to use the more general concept of random order values \parencite{weber1988probabilistic}.
    \Cref{sec:cooperative_game_weighted} takes a step in this direction by introducing bargaining weights and utilizing the weighted value.
}
This way of modelling bargaining outcomes has many precedents in the industrial organization literature \parencite[e.g.][]{montez2007downstream,hart1990property,levy1997individual,inderst2003bargaining,brugemann2019intra} and has a number of appealing properties.
For example, it is closely related to the marginal contributions of the players to the total value, and, as it will be shown, it is also quite intuitive in terms of comparative statistics.
Furthermore, and perhaps more importantly, there are a number of ways to place it on non-cooperative microfoundations by setting up non-cooperative games for which the Shapley value is a subgame perfect equilibrium \parencite[e.g.][]{gul1989bargaining,hart1996bargaining,stole1996organizational}.\footnote{
    For a possible microfoundation of this specific model, see \cref{sec:bargaining_microfoundation}.
}

@@

Let us now examine entry fees and fringe entry decisions in the benchmark model.
Recall that there is an infinity of potential fringe entrants looking to enter the market.
Therefore, total profits in equilibrium must be zero.
Combined with the  profit function, this gives the following expressions for the equilibrium number of fringe firms and the equilibrium size of the aggregate.
\begin{proposition}
    \label{prop:equilibrium_aggregate_benchmark}
    If entry costs $I_F$ and $F_F$ are low enough, the equilibrium size of the aggregate is
    \begin{align}
        A = \mu \frac{V_F}{F_F + I_F}.
        \label{eq:aggregate_eq}
    \end{align}
    and the equilibrium number of fringe firms is
    \begin{align*}
        N_F = \frac{\mu}{F_F + I_F} - N_P \frac{V_P}{V_F} - \frac{1}{V_F}.
    \end{align*}
    Otherwise,  $N_F = 0$ and the equilibrium size of the aggregate is
    \begin{align*}
        A = N_P V_P + 1.
    \end{align*}
\end{proposition}
Note that in the first case (\cref{eq:aggregate_eq}), the size of the aggregate does not depend on the platforms' product variety or the platform's product value.
The intuition behind this is that per-firm fringe profits only depend on these factors indirectly, through the size of the aggregate.
Therefore, the zero profit condition for the fringe firms pins down the aggregate in equilibrium (as long as the fringe is feasible).
That is, an increase in $N_P$ will simply replace some fringe entrants, but the free entry condition will pin down the same aggregate regardless of the number of platform products.

@@

\begin{theorem}
    \label{prop:optimal_entry_fee}
    The optimal entry fee when the platform is operating in the hybrid regime is unique and given by
    \begin{align*}
        F_F^* = \sqrt{\mu I_F V_F} - I_F.
    \end{align*}
    The platform's total profit in this case is
    \begin{align*}
        \pi_P^{t} = \mu - 2\sqrt{\frac{I_F \mu}{V_F}} + \frac{I_F}{V_F} (N_P V_P + 1).
    \end{align*}
    When the optimal mode of operation is retail, the platform's profit is
    \begin{align*}
        \pi_P^{t} = \pi_P^{v} = \mu \frac{ N_P V_P}{N_P V_P + 1}.
    \end{align*}
\end{theorem}

First, let us look at the case when the platform finds it optimal to operate in the hybrid regime.
Notice that the optimal entry fee does not depend on either the platform's product value or product variety (\cref{fig:entry_fee}).
This is because due to the lump-sum nature of the entry fee, the platform can extract all the surplus from the fringe firms, and thus chooses $F_F$ to maximize total industry profits.
The latter is essentially a function of the aggregate, minus the investment costs of the fringe firms.
As I have shown in \cref{prop:equilibrium_aggregate_benchmark}, the aggregate is independent of the platform's product variety in the hybrid regime, and therefore the optimal entry fee is also independent of it.

@@

The statements of these theorems are illustrated in \cref{fig:comparative_N_F} and \cref{fig:welfare_aggregate} and \cref{fig:platform_profits}.
The intuition behind these results can be demonstrated by looking at entry fees.
First, define the implied entry fee in the bargaining case as the difference between the variable profit and the final, total profit of the fringe firms (bar the investment cost):
\begin{align*}
    F_F^{\text{impl}} = \pi_F^v - \pi_F^t.
\end{align*}
As shown before, as the platform's product variety grows, its bargaining power also increases.
This can be thought of as an increase in (implied) entry fees $F_F^{\text{impl}}$, which in turn discourages fringe entry.
This is not happening in the benchmark model, as the optimal entry fee does not depend on the platform's product variety.
\Cref{fig:entry_fee} demonstrates this effect.

@@

                \addplot[draw=none,name path=hybrid] table[x=N_P,y=hybrid]{\equilibrium};
                \addplot[draw=none,name path=hybrid_bench] table[x=N_P,y=hybrid_bench]{\equilibrium};
                \addplot[draw=none,name path=bottom] {0};
                \addplot [fill=black, fill opacity=0.05] fill between [of=hybrid and bottom];
                \addplot [fill=black, fill opacity=0.05] fill between [of=hybrid_bench and bottom];
            \end{axis}
        \end{tikzpicture}
        \caption{Equilibrium number of fringe firms ($N_F$)}
        \label{fig:fringe_entry_eq}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.45\textwidth}
        \centering
        \begin{tikzpicture}
            \begin{axis}[
                    xlabel={$N_P$},
                    ylabel={$F_F$},
                    xmin=0, xmax=1.5, % adjust these values as needed
                    ymin=0, ymax=0.65, % adjust these values as needed
                    width=\linewidth, % adjust the width of the plot
                    axis lines=left,
                    xtick={0, 1.5},
                    legend pos=north east
                ]
                \addplot[color=myblue,mark=none,thick] table[x=N_P,y=F_F_opt]{\equilibrium};
                \addplot[color=myred,mark=none,thick] table[x=N_P,y=F_F_implied]{\equilibrium};
                \legend{Benchmark, Bargaining (implied)}

                \addplot[draw=none,name path=hybrid] table[x=N_P,y=hybrid]{\equilibrium};
                \addplot[draw=none,name path=hybrid_bench] table[x=N_P,y=hybrid_bench]{\equilibrium};
                \addplot[draw=none,name path=bottom] {0};
                \addplot [fill=black, fill opacity=0.05] fill between [of=hybrid and bottom];
                \addplot [fill=black, fill opacity=0.05] fill between [of=hybrid_bench and bottom];
            \end{axis}
        \end{tikzpicture}
        \caption{Optimal/implied entry fee ($F_F$)}
        \label{fig:entry_fee}
    \end{subfigure}
    \caption{Equilibrium number of fringe entrants and (implied) entry fees ($\mu = 1, N_C = 1, V_P = 1, V_F = 1, I_F = 0.2$). In the benchmark model, the entry fee does not depend on the platform's product variety, and an increase in $N_P$ leads to a proportional reduction in $N_F$. In contrast, in the bargaining case, the entry fee is increasing in $N_P$, and the reduction in $N_F$ is more than proportional. Dark shaded area represents hybrid mode under the bargaining assumption, while light shaded area represents additional hybrid mode under the benchmark assumption.}
    \label{fig:entry_and_fees}
\end{figure}

@@

                \addplot[draw=none,name path=hybrid] table[x=N_P,y=hybrid]{\equilibriumProfitOneSidedLowLambda};
                \addplot[draw=none,name path=hybrid_orig] table[x=N_P,y=hybrid]{\equilibrium};
                \addplot[draw=none,name path=bottom] {0};
                \addplot [fill=black, fill opacity=0.05] fill between [of=hybrid and bottom];
                \addplot [fill=black, fill opacity=0.05] fill between [of=hybrid_orig and bottom];
            \end{axis}
        \end{tikzpicture}
        \caption{Platform profits}
        \label{fig:platform_profits_low_lambda}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.45\textwidth}
        \centering
        \begin{tikzpicture}
            \begin{axis}[
                    xlabel={$N_P$},
                    ylabel={},
                    xmin=0, xmax=1.5, % adjust these values as needed
                    ymin=0, ymax=0.5, % adjust these values as needed
                    axis lines=left,
                    xtick={0, 1.5},
                    legend pos=south east,
                    width=\linewidth,
                ]
                \addplot[color=myblue,mark=none,thick] table[x=N_P,y=F_F_opt]{\equilibrium};
                \addplot[color=myred,mark=none,thick] table[x=N_P,y=F_F_implied]{\equilibrium};
                \addplot[color=mygreen,mark=none,thick] table[x=N_P,y=F_F_implied]{\equilibriumProfitOneSidedLowLambda};

@@

\begin{figure}
    \centering
    \begin{tikzpicture}[node distance=2cm, auto]
        \node[align=center] (entry_decision) {Potential entrants decide to invest \\ at cost $I_F$ \\ $[N_F]$};
        \node[align=center, draw, dashed] (entry_fee) [below of=entry_decision] {Entry fees are negotiated \\ between platform \\ and $N_F$ fringe firms \\ $[F_F]$};
        \node[align=center] (sales) [below of=entry_fee] {Platform and fringe \\ sell products \\ $[\pi_{Fi}^v, \pi_P^v]$};
        \node[align=center] (final) [below of=sales] {Final profits are realized \\ $[\pi_{Fi}^t, \pi_P^t]$};
        \draw[->] (entry_decision) -- (entry_fee);
        \draw[->] (entry_fee) -- (sales);
        \draw[->] (sales) -- (final);

        \node[align=center, right=of entry_decision, distance=3cm] (arrange_fringe) {Arrange fringe firms in some fixed order};
        \node[align=center, below of=arrange_fringe] (foreach) {For each (remaining) fringe firm $F_i$:};
        \node[align=center] (choose_proposer) [below=1cm of foreach] {$F_i$ or $P$ is choosen as the proposer};
        \node[align=center] (proposal) [below of=choose_proposer] {Proposer proposes entry fee $F_{F_i}$};
        \node[align=center] (accept) [below left=2cm and -2cm of proposal] {Responder accepts $F_{F_i}$};
        \node[align=center] (reject) [below right=2cm and -2cm of proposal] {Responder rejects $F_{F_i}$};
        \node[align=center] (next_player) [below of=accept] {Move on to the \\ next fringe firm};
        \node[align=center] (eliminate) [below of=reject] {Eliminate $F_i$};

@@

Then, for each fringe firm (following the order determined earlier), the platform and the fringe firm negotiate over the entry fee.
This bilateral negotiation follows the alternating offer procedure described in \textcite{binmore1986nash}.
One of the two players is chosen as a proposer, and can propose an entry fee for the given firm: $F_{F_i}$.
The other player can either accept or reject the proposal.

@@

The final piece that is needed to establish the interpretation in terms of entry fees is that for any given configuration of firms emerging from the bargaining process, and, crucially, regardless of the agreed upon entry fees, the unique equilibrium of the subsequent game is the one described in \cref{sec:results_demand}.
According to the previous theorem, players want to agree on a contract such that their final, total profits $\pi^t_{F_i}$ are equal to their Shapley value ($\varphi_{F_i}$).
Given any equilibrium sales profits ($\pi^v_{F_i}$), they can achieve it by setting the entry fees to $F_{F_i} = \varphi_{F_i} - \pi^v_{F_i}$.
Finally, \cref{sec:cooperative_game} and \cref{sec:results_demand} establish that both the Shapley value and the equilibrium sales profits are identical for each fringe firms, and thus a single, common entry fee $F_F$ will be agreed upon.

@@

\begin{proof}[Proof of \cref{prop:equilibrium_aggregate_benchmark}]
    From \cref{prop:optimal_profit}, the variable profit of each fringe firm is $\pi_{F_i}^{v*} = \mu V_F / A$.
    Total profit after entry fees and investment costs is therefore $\pi_{F_i}^{t*} = \mu V_F / A - I_F - F_F$.
    Under free entry, total profits are zero:
    \begin{align*}
        0 = \pi_{F_i}^{t*} = \mu V_F / A - F_F - I_F.
    \end{align*}
    Simple rearrangement gives the formula we are looking for,
    \begin{align*}
        A = \mu \frac{V_F}{F_F + I_F},
    \end{align*}
    and substituting in $A = N_P V_P + N_F V_F + 1$ yields the equilibrium number of fringe firms,
    \begin{align*}
        N_F = \frac{\mu}{F_F + I_F} - N_P \frac{V_P}{V_F} - \frac{1}{V_F}.
    \end{align*}
\end{proof}

>>>>

There is an infinite measure of fringe firms, who are deciding whether to enter the market.
Entering has two, separate costs: an exogenous investment cost $I_F$, and the lump-sum platform entry fee $K_F$.
One can conceptualize the first as usual fixed costs, such as the cost of setting up production, or designing a product.
Meanwhile, the second is a payment to the platform for using its services.
While percentage fees are more common both in the literature and in practice, I assume a lump-sum fee for a few reasons.
First, and most importantly, revenue-based fees enter the entrants' pricing decision, and thus create a channel through which platforms distort competition.
I want to show that even in the absence such distortions, hybrid platforms can have a significant impact on competition.
Furthermore, due to this distortion, the resulting game could not be represented as a transferable utility game, and the proposed solution concept would not be applicable.
Finally, lump-sum fees do make sense in settings when individual negotiation takes place and contracts are not standardized.

In the benchmark model, the game starts by the platform announcing and committing to an entry fee $K_F$.\footnote{
    With no commitment power, but the ability to set any prices after fringe firms make their investment decisions, the platform would charge an entry fee that would make the fringe profits zero \emph{sans the investment cost}.
    This would lead to a trivial equilibrium, where no firm enters.
}
In the bargaining case, the platform cannot commit to entry fees at this point.
Next, each fringe firm decides whether to create a product at cost $I_F$ and enter the market.
In the bargaining model, the entry fee is decided at this point as a result of some negotiation\footnote{
    The negotiation process, or rather its outcome is described in detail in \cref{sec:cooperative_game}.
} between the platform and the firms that have made the investment.
After this, the firms that made the investment pay the platform entry fees, too.

@@

The main difference between the benchmark and the bargaining model is in determining the entry fee $K_F$.
In the former, the platform unilaterally sets the fee, and the fringe treats it as a take it or leave it offer.
On the other hand, in the bargaining model, I assume that the entry fee is the result of a negotiation between the parties.
\Cref{fig:timing} illustrates this difference.

\begin{figure}
    \centering
    \begin{subfigure}{0.45\textwidth}
        \centering
        \begin{tikzpicture}[node distance=2cm, auto]
            \node[align=center] (entry_fee) {Platform unilaterally sets the entry fee \\ $[K_F]$};
            \node[align=center] (entry_decision) [below of=entry_fee] {Potential entrants decide to enter \\ at cost $I_F + K_F$ \\ $[N_F]$};
            \node[align=center] (sales) [below of=entry_decision] {Platform and fringe sell products \\ $[\pi_{Fi}^v, \pi_P^v]$};
            \node[align=center] (final) [below of=sales] {Final profits are realized \\ $[\pi_{Fi}^t, \pi_P^t]$};
            \draw[->] (entry_fee) -- (entry_decision);
            \draw[->] (entry_decision) -- (sales);
            \draw[->] (sales) -- (final);
        \end{tikzpicture}
        \caption{Benchmark model (platform sets the entry fee unilaterally)}
    \end{subfigure}
    \hfill
    \begin{subfigure}{0.45\textwidth}
        \centering
        \begin{tikzpicture}[node distance=2cm, auto]
            \node[align=center] (entry_decision) {Potential entrants decide to invest \\ at cost $I_F$ \\ $[N_F]$};
            \node[align=center] (entry_fee) [below of=entry_decision] {Entry fees are negotiated \\ between platform and $N_F$ fringe firms \\ $[K_F]$};
            \node[align=center] (sales) [below of=entry_fee] {Platform and fringe sell products \\ $[\pi_{Fi}^v, \pi_P^v]$};
            \node[align=center] (final) [below of=sales] {Final profits are realized \\ $[\pi_{Fi}^t, \pi_P^t]$};
            \draw[->] (entry_decision) -- (entry_fee);
            \draw[->] (entry_fee) -- (sales);
            \draw[->] (sales) -- (final);
        \end{tikzpicture}
        \caption{Bargaining model (platform and fringe negotiate over the entry fee)}
    \end{subfigure}
    \caption{Timing of the models}
    \label{fig:timing}
\end{figure}

@@

I assume that there is a continuum of potential fringe entrants, indexed by $i \in \mathbb{R}^+_0$.
Each of them can create a product at an exogenous investment cost $I_F$.
If they decide not to, they make zero profits and do not participate in the later stages of the game.
Furthermore, these firms can only sell their products through the platform, for which the platform can charge a lump-sum entry fee $K_F$.
The timing of these decisions is as follows: (1) the platform sets and commits to an entry fee $K_F$, (2) the fringe firms decide whether to enter the market, and (3) the firms that have entered pay the entry fee to the platform.

@@

In order to keep the model tractable I model the negotiation process in a reduced form manner.
In particular, I assume that the platform and the entrants agree on an entry fee $K_F$, which makes the total profits net entry fees equal to the Shapley value of the players.\footnote{
    One simple extension would be to use the more general concept of random order values \parencite{weber1988probabilistic}.
    \Cref{sec:cooperative_game_weighted} takes a step in this direction by introducing bargaining weights and utilizing the weighted value.
}
This way of modelling bargaining outcomes has many precedents in the industrial organization literature \parencite[e.g.][]{montez2007downstream,hart1990property,levy1997individual,inderst2003bargaining,brugemann2019intra} and has a number of appealing properties.
For example, it is closely related to the marginal contributions of the players to the total value, and, as it will be shown, it is also quite intuitive in terms of comparative statistics.
Furthermore, and perhaps more importantly, there are a number of ways to place it on non-cooperative microfoundations by setting up non-cooperative games for which the Shapley value is a subgame perfect equilibrium \parencite[e.g.][]{gul1989bargaining,hart1996bargaining,stole1996organizational}.\footnote{
    For a possible microfoundation of this specific model, see \cref{sec:bargaining_microfoundation}.
}

@@

Let us now examine entry fees and fringe entry decisions in the benchmark model.
Recall that there is an infinity of potential fringe entrants looking to enter the market.
Therefore, total profits in equilibrium must be zero.
Combined with the  profit function, this gives the following expressions for the equilibrium number of fringe firms and the equilibrium size of the aggregate.
\begin{proposition}
    \label{prop:equilibrium_aggregate_benchmark}
    If entry costs $I_F$ and $K_F$ are low enough, the equilibrium size of the aggregate is
    \begin{align}
        A = \mu \frac{V_F}{K_F + I_F}.
        \label{eq:aggregate_eq}
    \end{align}
    and the equilibrium number of fringe firms is
    \begin{align*}
        N_F = \frac{\mu}{K_F + I_F} - N_P \frac{V_P}{V_F} - \frac{1}{V_F}.
    \end{align*}
    Otherwise,  $N_F = 0$ and the equilibrium size of the aggregate is
    \begin{align*}
        A = N_P V_P + 1.
    \end{align*}
\end{proposition}
Note that in the first case (\cref{eq:aggregate_eq}), the size of the aggregate does not depend on the platforms' product variety or the platform's product value.
The intuition behind this is that per-firm fringe profits only depend on these factors indirectly, through the size of the aggregate.
Therefore, the zero profit condition for the fringe firms pins down the aggregate in equilibrium (as long as the fringe is feasible).
That is, an increase in $N_P$ will simply replace some fringe entrants, but the free entry condition will pin down the same aggregate regardless of the number of platform products.

@@

\begin{theorem}
    \label{prop:optimal_entry_fee}
    The optimal entry fee when the platform is operating in the hybrid regime is unique and given by
    \begin{align*}
        K_F^* = \sqrt{\mu I_F V_F} - I_F.
    \end{align*}
    The platform's total profit in this case is
    \begin{align*}
        \pi_P^{t} = \mu - 2\sqrt{\frac{I_F \mu}{V_F}} + \frac{I_F}{V_F} (N_P V_P + 1).
    \end{align*}
    When the optimal mode of operation is retail, the platform's profit is
    \begin{align*}
        \pi_P^{t} = \pi_P^{v} = \mu \frac{ N_P V_P}{N_P V_P + 1}.
    \end{align*}
\end{theorem}

First, let us look at the case when the platform finds it optimal to operate in the hybrid regime.
Notice that the optimal entry fee does not depend on either the platform's product value or product variety (\cref{fig:entry_fee}).
This is because due to the lump-sum nature of the entry fee, the platform can extract all the surplus from the fringe firms, and thus chooses $K_F$ to maximize total industry profits.
The latter is essentially a function of the aggregate, minus the investment costs of the fringe firms.
As I have shown in \cref{prop:equilibrium_aggregate_benchmark}, the aggregate is independent of the platform's product variety in the hybrid regime, and therefore the optimal entry fee is also independent of it.

@@

The statements of these theorems are illustrated in \cref{fig:comparative_N_F} and \cref{fig:welfare_aggregate} and \cref{fig:platform_profits}.
The intuition behind these results can be demonstrated by looking at entry fees.
First, define the implied entry fee in the bargaining case as the difference between the variable profit and the final, total profit of the fringe firms (bar the investment cost):
\begin{align*}
    K_F^{\text{impl}} = \pi_F^v - \pi_F^t.
\end{align*}
As shown before, as the platform's product variety grows, its bargaining power also increases.
This can be thought of as an increase in (implied) entry fees $K_F^{\text{impl}}$, which in turn discourages fringe entry.
This is not happening in the benchmark model, as the optimal entry fee does not depend on the platform's product variety.
\Cref{fig:entry_fee} demonstrates this effect.

@@

                \addplot[draw=none,name path=hybrid] table[x=N_P,y=hybrid]{\equilibrium};
                \addplot[draw=none,name path=hybrid_bench] table[x=N_P,y=hybrid_bench]{\equilibrium};
                \addplot[draw=none,name path=bottom] {0};
                \addplot [fill=black, fill opacity=0.05] fill between [of=hybrid and bottom];
                \addplot [fill=black, fill opacity=0.05] fill between [of=hybrid_bench and bottom];
            \end{axis}
        \end{tikzpicture}
        \caption{Equilibrium number of fringe firms ($N_F$)}
        \label{fig:fringe_entry_eq}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.45\textwidth}
        \centering
        \begin{tikzpicture}
            \begin{axis}[
                    xlabel={$N_P$},
                    ylabel={$K_F$},
                    xmin=0, xmax=1.5, % adjust these values as needed
                    ymin=0, ymax=0.65, % adjust these values as needed
                    width=\linewidth, % adjust the width of the plot
                    axis lines=left,
                    xtick={0, 1.5},
                    legend pos=north east
                ]
                \addplot[color=myblue,mark=none,thick] table[x=N_P,y=K_F_opt]{\equilibrium};
                \addplot[color=myred,mark=none,thick] table[x=N_P,y=K_F_implied]{\equilibrium};
                \legend{Benchmark, Bargaining (implied)}

                \addplot[draw=none,name path=hybrid] table[x=N_P,y=hybrid]{\equilibrium};
                \addplot[draw=none,name path=hybrid_bench] table[x=N_P,y=hybrid_bench]{\equilibrium};
                \addplot[draw=none,name path=bottom] {0};
                \addplot [fill=black, fill opacity=0.05] fill between [of=hybrid and bottom];
                \addplot [fill=black, fill opacity=0.05] fill between [of=hybrid_bench and bottom];
            \end{axis}
        \end{tikzpicture}
        \caption{Optimal/implied entry fee ($K_F$)}
        \label{fig:entry_fee}
    \end{subfigure}
    \caption{Equilibrium number of fringe entrants and (implied) entry fees ($\mu = 1, N_C = 1, V_P = 1, V_F = 1, I_F = 0.2$). In the benchmark model, the entry fee does not depend on the platform's product variety, and an increase in $N_P$ leads to a proportional reduction in $N_F$. In contrast, in the bargaining case, the entry fee is increasing in $N_P$, and the reduction in $N_F$ is more than proportional. Dark shaded area represents hybrid mode under the bargaining assumption, while light shaded area represents additional hybrid mode under the benchmark assumption.}
    \label{fig:entry_and_fees}
\end{figure}

@@

                \addplot[draw=none,name path=hybrid] table[x=N_P,y=hybrid]{\equilibriumProfitOneSidedLowLambda};
                \addplot[draw=none,name path=hybrid_orig] table[x=N_P,y=hybrid]{\equilibrium};
                \addplot[draw=none,name path=bottom] {0};
                \addplot [fill=black, fill opacity=0.05] fill between [of=hybrid and bottom];
                \addplot [fill=black, fill opacity=0.05] fill between [of=hybrid_orig and bottom];
            \end{axis}
        \end{tikzpicture}
        \caption{Platform profits}
        \label{fig:platform_profits_low_lambda}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.45\textwidth}
        \centering
        \begin{tikzpicture}
            \begin{axis}[
                    xlabel={$N_P$},
                    ylabel={},
                    xmin=0, xmax=1.5, % adjust these values as needed
                    ymin=0, ymax=0.5, % adjust these values as needed
                    axis lines=left,
                    xtick={0, 1.5},
                    legend pos=south east,
                    width=\linewidth,
                ]
                \addplot[color=myblue,mark=none,thick] table[x=N_P,y=K_F_opt]{\equilibrium};
                \addplot[color=myred,mark=none,thick] table[x=N_P,y=K_F_implied]{\equilibrium};
                \addplot[color=mygreen,mark=none,thick] table[x=N_P,y=K_F_implied]{\equilibriumProfitOneSidedLowLambda};

@@

\begin{figure}
    \centering
    \begin{tikzpicture}[node distance=2cm, auto]
        \node[align=center] (entry_decision) {Potential entrants decide to invest \\ at cost $I_F$ \\ $[N_F]$};
        \node[align=center, draw, dashed] (entry_fee) [below of=entry_decision] {Entry fees are negotiated \\ between platform \\ and $N_F$ fringe firms \\ $[K_F]$};
        \node[align=center] (sales) [below of=entry_fee] {Platform and fringe \\ sell products \\ $[\pi_{Fi}^v, \pi_P^v]$};
        \node[align=center] (final) [below of=sales] {Final profits are realized \\ $[\pi_{Fi}^t, \pi_P^t]$};
        \draw[->] (entry_decision) -- (entry_fee);
        \draw[->] (entry_fee) -- (sales);
        \draw[->] (sales) -- (final);

        \node[align=center, right=of entry_decision, distance=3cm] (arrange_fringe) {Arrange fringe firms in some fixed order};
        \node[align=center, below of=arrange_fringe] (foreach) {For each (remaining) fringe firm $F_i$:};
        \node[align=center] (choose_proposer) [below=1cm of foreach] {$F_i$ or $P$ is choosen as the proposer};
        \node[align=center] (proposal) [below of=choose_proposer] {Proposer proposes entry fee $K_{F_i}$};
        \node[align=center] (accept) [below left=2cm and -2cm of proposal] {Responder accepts $K_{F_i}$};
        \node[align=center] (reject) [below right=2cm and -2cm of proposal] {Responder rejects $K_{F_i}$};
        \node[align=center] (next_player) [below of=accept] {Move on to the \\ next fringe firm};
        \node[align=center] (eliminate) [below of=reject] {Eliminate $F_i$};

@@

Then, for each fringe firm (following the order determined earlier), the platform and the fringe firm negotiate over the entry fee.
This bilateral negotiation follows the alternating offer procedure described in \textcite{binmore1986nash}.
One of the two players is chosen as a proposer, and can propose an entry fee for the given firm: $K_{F_i}$.
The other player can either accept or reject the proposal.

@@

The final piece that is needed to establish the interpretation in terms of entry fees is that for any given configuration of firms emerging from the bargaining process, and, crucially, regardless of the agreed upon entry fees, the unique equilibrium of the subsequent game is the one described in \cref{sec:results_demand}.
According to the previous theorem, players want to agree on a contract such that their final, total profits $\pi^t_{F_i}$ are equal to their Shapley value ($\varphi_{F_i}$).
Given any equilibrium sales profits ($\pi^v_{F_i}$), they can achieve it by setting the entry fees to $K_{F_i} = \varphi_{F_i} - \pi^v_{F_i}$.
Finally, \cref{sec:cooperative_game} and \cref{sec:results_demand} establish that both the Shapley value and the equilibrium sales profits are identical for each fringe firms, and thus a single, common entry fee $K_F$ will be agreed upon.

\section{The platform's product pricing assumption}
\label{sec:separate_pricing}

TODO: discuss the assumptioin of pricing products separately

@@

\begin{proof}[Proof of \cref{prop:equilibrium_aggregate_benchmark}]
    From \cref{prop:optimal_profit}, the variable profit of each fringe firm is $\pi_{F_i}^{v*} = \mu V_F / A$.
    Total profit after entry fees and investment costs is therefore $\pi_{F_i}^{t*} = \mu V_F / A - I_F - K_F$.
    Under free entry, total profits are zero:
    \begin{align*}
        0 = \pi_{F_i}^{t*} = \mu V_F / A - K_F - I_F.
    \end{align*}
    Simple rearrangement gives the formula we are looking for,
    \begin{align*}
        A = \mu \frac{V_F}{K_F + I_F},
    \end{align*}
    and substituting in $A = N_P V_P + N_F V_F + 1$ yields the equilibrium number of fringe firms,
    \begin{align*}
        N_F = \frac{\mu}{K_F + I_F} - N_P \frac{V_P}{V_F} - \frac{1}{V_F}.
    \end{align*}
\end{proof}

\begin{proof}[Proof of \cref{prop:optimal_entry_fee}]
    The total profit function of the platform is the following:
    \begin{align*}
        \pi_P^t &= \pi_P^v + K_F N_F \\
        &= \mu \frac{N_P V_P}{K_F + I_F} + K_F \left[ \frac{\mu}{K_F + I_F} - N_P \frac{V_P}{V_F} - \frac{1}{V_F} \right].
    \end{align*}
    The function is strictly concave in $K_F$, so the first order condition is sufficient for optimality in the case of an interior solution.
    Assume that that the optimum is indeed interior.
    Then the FOC is
    \begin{align*}
        \frac{\mu I_F V_F - (K_F + I_F)^2}{V_F (K_F + I_F)^2} = 0.
    \end{align*}
    Rearranging it gives the optimal entry fee
    \begin{align*}
        K_F^* = \sqrt{\mu I_F V_F} - I_F,
    \end{align*}
    and substituting it into the profit function leads to
    \begin{align*}
        \pi_P^{*t} = \mu - 2\sqrt{\frac{I_F \mu}{V_F}} + \frac{I_F}{V_F} (N_P V_P + 1).
    \end{align*}
    Finally, note that
    \begin{align*}
        \pi_P^{*t} \geq \mu \frac{N_P V_P}{N_P V_P + 1},
    \end{align*}
    i.e., the profit that the platform could achieve by excluding the fringe completely.
    Therefore, the optimum is indeed interior whenever $K_F$ is low enough

    Now consider the case when $K_F^*$ is so large that it would lead to no fringe entry.
    In that case, the platform's only source of profit is selling its own products, and thus
    \begin{align*}
        \pi_P^{t} = \pi_P^{v} = \mu \frac{ N_P V_P}{N_P V_P + 1}.
    \end{align*}
\end{proof}
